\documentclass{tccv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\begin{document}

\part{Simone Robutti}

\begin{eventlist}

\item{Jan 2022 - Dec 2023}
     {AI Forensics}
     {Data Engineer, Organization Designer}

First year: organizational development of all the decision-making and operational processes and institutions of AI Forensics. Second year: development of an end-to-end experiment platform to interrogate LLM chatbots and RAG systems (i.e. Bing Chat, Bard). Leadership of a project investigating the impact of LLMs on electoral integrity in Switzerland and Bavaria.

\item{Mar 2017- Dec 2021}
     {Teraki, Berlin}
     {Team Leader, BE+ML engineer}

Development of user-facing REST API Platform to run proprietary ML pipelines on small and big user datasets. Development of internal tools for Data Scientists. In-depth testing of REST API. Maintenance of development tools, CI and CD. Productization of ML algorithms developed by the data scientist. Coordination of the BE team. Involvement in planning and analysis activities alongside other team leaders and C-level.


\item{Nov 2016- Jan 2017}
     {MotionLogic, Berlin}
     {Data Engineer}

Development of the company's core product: a system to ingest and process cellular network signals to extract information through ad-hoc models. Productization of existing algorithms developed by the Data Science Team, development of new models on my own, development of a data quality monitoring system, performance optimization.


\noindent\hfil\rule{0.3\textwidth}{.4pt}

\item{Feb 2016 - Nov 2016}
{Databiz - Radicalbit, Milan}
{Machine Learning Engineer}

As the only Machine Learning Engineer, my work involved designing new solutions for our customers to make use of Flink, core component of our distribution. Also, I've been involved in the open-source development of FlinkML and FlinkJPMML.

\noindent\hfil\rule{0.3\textwidth}{.4pt}

\item{Apr 2015 - Feb 2016}
{Databiz, Milan}
{Machine Learning Engineer}

Design and implementation of a near-real-time scoring streaming system using Apache Spark, Knime, Hbase, JPPML, Hive.

\end{eventlist}

\personal
    [https://github.com/chobeat/]
    {Keibelstr. 37, 10178, Berlin}
    {simone.robutti@gmail.com}
    {https://robutti.me}

\section{Education}

\begin{yearlist}

\item[Master Degree]{2012-2015}
     {Computer Science}
     {Università degli Studi di Milano}

\item[Bachelor Degree]{2007-2012}
{Computer Science}
{Università degli Studi di Milano}

\item[High School Diploma]{2002-2007}
{Scientific specialization}
{Liceo Galileo Galilei, Alessandria}



\end{yearlist}

\section{Public projects}

\begin{yearlist}

\item{2021}
     {mobilizon-reshare (\href{https://github.com/Tech-Workers-Coalition-Italia/mobilizon-reshare}{github.com/Tech-Workers-Coalition-Italia/mobilizon-reshare})}
     {Suite for automated event promotion on social media}
\item{2019}
     {pyscaffoldext-custom-extension  (\href{github.com/pyscaffold/pyscaffoldext-custom-extension})}
     {Pyscaffold extension to create pyscaffold extensions}
\item{2017}
     {scala-json-feed (\href{https://github.com/chobeat/scala-json-feed}{github.com/chobeat/scala-json-feed})}
     {Scala library for JSON Feed}


\end{yearlist}

\section{Technical skills}

\begin{factlist}

\item{Technical}
     {Python, Scala, Docker, Airflow, fastapi, Spark, Flink, SQL, MongoDB, SQLITE, PostgreSQL, InfluxDB, Grafana, pandas, matplotlib, GraphQL, Appium, git, yarn, JSON, maven, sbt, setuptools, tox, poetry}

\item{Organizational}
{Sociocracy, Holacracy, Ecosystemic Design, Agile, Governance Design, Process Design, Process Mapping, Strategy Development, Nonviolent Communication}


\item{No Code}
     {Notion, Airtable, Zapier, Strapi, n8n}

\item{Studying}
    {Typescript, Rust, Elixir, Diffusion Models, 3EO}

\end{factlist}

\end{document}
